The problem and promise of scale in animal social multilayer networks

### 2020-02-10 paper/manuscript.Rmd
fiddly refs

Our study is motivated by behavioural, landscape, and spatial ecology to build a
conceptual and analytical framework for scale-dependent multilayer networks and
we apply this framework to a case study of caribou (*Rangifer tarandus*) in
Newfoundland, Canada [@Peignier_2019]. We use this case study to address two
principal questions associated with scale-dependent multilayer networks. First,
to what degree does the social scale of relationships, spatial scale of
landscapes, and temporal scale of analysis influence our ability to interpret
complex social systems? Second, can variation in the social, spatial, and temporal
improve predictions associated with biological differences in seasonal resource
availability and social association? We conclude with perspectives for further
development and application of scale in multilayer networks with respect to 
phenotypes and individual fitness [@Webber_2018] <!-- TODO: ref should be 2018, but defaulting to 2017-->, 
movement ecology and collective
movement [@Jolles_2019], and habitat selection and space use. <!-- TODO: (REF)-->

>>>>

Our study is motivated by behavioural, landscape, and spatial ecology to build a
conceptual and analytical framework for scale-dependent multilayer networks and
we apply this framework to a case study of caribou (*Rangifer tarandus*) in
Newfoundland, Canada [@Peignier_2019]. We use this case study to address two
principal questions associated with scale-dependent multilayer networks. First,
to what degree does the social scale of relationships, spatial scale of
landscapes, and temporal scale of analysis influence our ability to interpret
complex social systems? Second, can variation in the social, spatial, and
temporal improve predictions associated with biological differences in seasonal
resource availability and social association? We conclude with perspectives for
further development and application of scale in multilayer networks with respect
to phenotypes and individual fitness [@Webber_2018], movement ecology and
collective movement [@Jolles_2019], and habitat selection and space use. <!--
TODO: (REF)--> <!-- TODO: Webber reference should be 2018, but defaulting to
2017-->
